Title

### 2011-09-24 ms_model.tex
Added license information to the top of each of the files that contain my content
Work towards mathematical model
fixed typo and added index on "coordinate vector"

@@

Distribution function:
\begin{equation}
  f(\vec{r}, \vec{p}; t) = C(t)\exp \left[ - \Gamma(\vec{r}, \vec{p}; t) \right]
\end{equation}
where
\begin{equation}
  \Gamma(\vec{r}, \vec{p}; t) =
  \frac{x^2 + y^2}{2 \sigma_{\smallT}} + \frac{z^2}{2 \sigma_{z}}
  + \frac{
    [p_x - (\gamma_{\smallT}/\sigma_{\smallT}) x ]^2 
    + [p_y - (\gamma_{\smallT}/\sigma_{\smallT}) y ]^2
  }{2 \eta_{\smallT}}
  + \frac{ [p_z - (\gamma_{z}/\sigma_{z}) z ]^2 }{2 \eta_{z}}
\end{equation}
In this form, the normalization constant, given by
\begin{equation}
  \int f(\vec{r}, \vec{p}; t) d\vec{r} d\vec{p} = N
\end{equation}
is
\begin{equation}
  C(t) = \frac{N}{(2\pi)^3} 
  \left( 
    \frac{1}{\sigma_{\smallT}^2\eta_{\smallT}^2\sigma_{z}\eta_{z}}
  \right)^{\frac{1}{2}}
\end{equation}
These equations may be viewed from a matrix perspective if we define the ``coordinate vection'' $u = (x, p_x, y, p_y, z, p_z)$. In this space,
\begin{equation}
  \Gamma(\vec{r}, \vec{p}; t) = \frac{1}{2}\sum\limits_{ij} A_{ij} u_i u_j
\end{equation}
where
\begin{equation}
  A = 
  \begin{pmatrix}
    a_{\smallT} & 0 & 0 \\
    0 & a_{\smallT} & 0 \\
    0 & 0 & a_{z}
  \end{pmatrix}
  \qquad \text{and} \qquad
  a_{\alpha} = 
  \begin{pmatrix}
    1/\sigma_{\alpha} + \gamma_{\alpha}^2/(\eta_{\alpha} \sigma_{\alpha}) & \gamma_{\alpha}/(\eta_{\alpha} \sigma_{\alpha}) \\
    \gamma_{\alpha}/(\eta_{\alpha} \sigma_{\alpha}) & 1/\eta_{\alpha}
  \end{pmatrix}
\end{equation}
with ${\scriptstyle \alpha} = \smallT \text{ or } z$. This form allows the isolation of any of the six parameters using
\begin{equation}
  (A^{-1})_{ij} = \frac{1}{N} \int f(\vec{r}, \vec{p}; t) d\vec{r} d\vec{p}
\end{equation}
which yields
\begin{equation}
  A = 
  \begin{pmatrix}
    a_{\smallT}^{-1} & 0 & 0 \\
    0 & a_{\smallT}^{-1} & 0 \\
    0 & 0 & a_{z}^{-1}
  \end{pmatrix}
  \qquad \text{and} \qquad
  a_{\alpha} = 
  \begin{pmatrix}
    \sigma_{\alpha} & \gamma_{\alpha} \\
    \gamma_{\alpha} & \eta_{\alpha} + \gamma_{\alpha}^2/\sigma_{\alpha}
  \end{pmatrix}
\end{equation}

>>>>

%This work is licensed under the Creative Commons Attribution-NonCommercial-NoDerivs 3.0 United States License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-nd/3.0/us/ or send a letter to Creative Commons, 444 Castro Street, Suite 900, Mountain View, California, 94041, USA.

@@

Distribution function:
\begin{equation}
  f(\vec{r}, \vec{p}; t) = C(t)\exp \left[ - \Gamma(\vec{r}, \vec{p}; t) \right]
\end{equation}
where
\begin{equation}
  \Gamma(\vec{r}, \vec{p}; t) =
  \frac{x^2 + y^2}{2 \sigma_{\smallT}} + \frac{z^2}{2 \sigma_{z}}
  + \frac{
    [p_x - (\gamma_{\smallT}/\sigma_{\smallT}) x ]^2 
    + [p_y - (\gamma_{\smallT}/\sigma_{\smallT}) y ]^2
  }{2 \eta_{\smallT}}
  + \frac{ [p_z - (\gamma_{z}/\sigma_{z}) z ]^2 }{2 \eta_{z}}
\end{equation}
In this form, the normalization constant, given by
\begin{equation}
  \int f(\vec{r}, \vec{p}; t) d\vec{r} d\vec{p} = N
\end{equation}
is
\begin{equation}
  C(t) = \frac{N}{(2\pi)^3} 
  \left( 
    \frac{1}{\sigma_{\smallT}^2\eta_{\smallT}^2\sigma_{z}\eta_{z}}
  \right)^{\frac{1}{2}}
\end{equation}
These equations may be viewed from a matrix perspective if we define the ``coordinate vector'' $u_i = (x, p_x, y, p_y, z, p_z)$. In this space,
\begin{equation}
  \Gamma(\vec{r}, \vec{p}; t) = \frac{1}{2}\sum\limits_{ij} A_{ij} u_i u_j
\end{equation}
where
\begin{equation}
  A = 
  \begin{pmatrix}
    a_{\smallT} & 0 & 0 \\
    0 & a_{\smallT} & 0 \\
    0 & 0 & a_{z}
  \end{pmatrix}
  \qquad \text{and} \qquad
  a_{\alpha} = 
  \begin{pmatrix}
    1/\sigma_{\alpha} + \gamma_{\alpha}^2/(\eta_{\alpha} \sigma_{\alpha}) & \gamma_{\alpha}/(\eta_{\alpha} \sigma_{\alpha}) \\
    \gamma_{\alpha}/(\eta_{\alpha} \sigma_{\alpha}) & 1/\eta_{\alpha}
  \end{pmatrix}
\end{equation}
with ${\scriptstyle \alpha} = \smallT \text{ or } z$. This form allows the isolation of any of the six parameters using
\begin{equation}
  (A^{-1})_{ij} = \frac{1}{N} \int f(\vec{r}, \vec{p}; t) d\vec{r} d\vec{p}
\end{equation}
which yields
\begin{equation}
  A = 
  \begin{pmatrix}
    a_{\smallT}^{-1} & 0 & 0 \\
    0 & a_{\smallT}^{-1} & 0 \\
    0 & 0 & a_{z}^{-1}
  \end{pmatrix}
  \qquad \text{and} \qquad
  a^{-1}_{\alpha} = 
  \begin{pmatrix}
    \sigma_{\alpha} & \gamma_{\alpha} \\
    \gamma_{\alpha} & \eta_{\alpha} + \gamma_{\alpha}^2/\sigma_{\alpha}
  \end{pmatrix}
\end{equation}
Taking the time derivative of the components of $A^{-1}$
\begin{equation}
  \frac{d}{dt} a^{-1}_{\alpha} = 
  \begin{pmatrix}
    \dfrac{d\sigma_{\alpha}}{dt} & \dfrac{d\gamma_{\alpha}}{dt} \\
    \dfrac{d\gamma_{\alpha}}{dt} & \dfrac{d\eta_{\alpha}}{dt} + 2\dfrac{\gamma_{\alpha}}{\sigma_{\alpha}}\dfrac{d\gamma_{\alpha}}{dt}- \dfrac{\gamma^{2}_{\alpha}}{\sigma^{2}_{\alpha}}\dfrac{d\sigma_{\alpha}}{dt}
  \end{pmatrix}
\end{equation}
